Chronic imaging of cortical oxygen tension and blood flow after targeted vascular occlusion

### 2018-04-16 article.tex
Defined rCFB

Each inverse correlation time sequence was then baselined against the first frame to calculate an estimate of relative change in blood flow ($\rfrac{\tau_{c,initial}}{\tau_{c,current}}$) \cite{Kazmi:2015du}. Because $\beta$ is a property of the instrumentation and should not vary throughout the course of an experiment, it was assumed $\beta = 1$. The same regions of interest defined for DMD structured illumination were then used to calculate timecourses of the relative change in flow.

>>>>

Each inverse correlation time sequence was then baselined against the first frame to calculate an estimate of relative change in blood flow ($rCFB = \rfrac{\tau_{c,initial}}{\tau_{c,current}}$) \cite{Kazmi:2015du}. Because $\beta$ is a property of the instrumentation and should not vary throughout the course of an experiment, it was assumed $\beta = 1$. The same regions of interest defined for DMD structured illumination were then used to calculate timecourses of the relative change in flow.
